Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-08-13 Methods.tex
Medians

Measurements were taken at the end of 1000 rounds of play, and emulators were built against the mean, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.

Twelve emulators were built, covering each of the four output on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

>>>>

Measurements were taken at the end of 1000 rounds of play, and emulators were built against the median, and interquartile range of each measure to assess both the overall trend, and the extent to which the parameters contribute to variance between runs.

Sixteen emulators were built, covering each of the four outputs on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.
